### 2019-03-26 jpdc/tex/abstract.tex
Add jpdc.

\begin{abstract}

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constraints, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
The FRQ models utilization of resources and predicts the execution time of computing jobs on different DAG frameworks. 
We use the FRQ model to assist in analyzing DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

>>>>

\begin{abstract}[S U M M A R Y]

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constraints, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

% Short abstract 100
% To optimize shuffle overhead in the DAG computing frameworks, we present SCache, an open source plug-in system. We also propose a new performance model called Framework Resources Quantification(FRQ) model. The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of jobs. We use the model to analyze the deficiencies of the frameworks. SCache uses a heuristic pre-scheduling algorithm to pre-fetch shuffle data. Meanwhile, SCache uses memory to accelerate the shuffle process. We have implemented SCache on both Spark and Hadoop MapReduce. The performance of SCache has been evaluated on a 50-node Amazon EC2 cluster.

### 2019-03-26 jpdc/tex/evaluation.tex
Add jpdc.

% Because a complex Spark application consists of multiple stages. The completion time of each stage varies under different input data, configurations and different number of stages. This uncertainty leads to the dilemma that dramatic fluctuation occurs in overall performance comparison. To present a straightforward illustration, we limit the scope of most evaluations in a single stage.
\begin{figure*}
	\centering
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbymapstage}
				\caption{Map Stage Completion Time}
				\label{fig:mapstage}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbyreducestage}
				\caption{Reduce Stage Completion Time\newline}
				\label{fig:reducestage}	
			\end{minipage}
		\end{subfigure}
		\caption{Stage Completion Time of Single Shuffle Test}
		\label{fig:singleshuffle}
	\end{minipage}	
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbymaptask}
				\caption{Median Task in Map Stages}
				\label{fig:maptask}
			\end{minipage}

			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbyreducetask}
				\caption{Median Task in Reduce Stages\newline}
				\label{fig:reducetask}
			\end{minipage}
		\end{subfigure}
		\caption{Median Task Completion Time of Single Shuffle Test}
		\label{fig:singleshuffletask}
	\end{minipage}	
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/tera}
				\caption{Reduce Stage of First Shuffle}
				\label{fig:terasort}
			\end{minipage}

			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/tera_shuffle}
				\caption{Network Traffic of Second Shuffle}
				\label{fig:terashuffle}
			\end{minipage}
		\end{subfigure}
		\caption{Terasort Evaluation}
	\end{minipage}
\end{figure*}

@@

In the reduce task, most of the shuffle overhead is introduced by network transfer delay. 
By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
The in-memory cache of shuffle data further reduce the shuffle read time. 
As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
In addition, the heuristic algorithm can achieve a balanced pre-scheduling result, thus providing ~$80\%$ improvement in reduce stage completion time (Figure \ref{fig:reducestage}).

@@

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure}
	\centering
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
		\caption{\color{blue}Hadoop MapReduce with SCache}
		\label{fig:hadoop_terasort_scache}
	\end{subfigure}
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
		\caption{\color{blue}Hadoop MapReduce without SCache}
		\label{fig:hadoop_terasort_origin}
	\end{subfigure}
	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
	\label{fig:hadoop_terasort}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=.9\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
        \caption{\color{blue}Hadoop MapReduce Terasort completion time}
		\label{fig:hadoop_terasort_time}
    \end{minipage}\hfill
    \begin{minipage}{0.42\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/sampling} % second figure itself
        \caption{Sampling Overhead}
		\label{fig:sampling}
    \end{minipage}
\end{figure}

>>>>

% Because a complex Spark application consists of multiple stages. The completion time of each stage varies under different input data, configurations and different number of stages. This uncertainty leads to the dilemma that dramatic fluctuation occurs in overall performance comparison. To present a straightforward illustration, we limit the scope of most evaluations in a single stage.
\begin{figure*}
	\centering
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbymapstage}
				\caption{Map Stage Completion Time}
				\label{fig:mapstage}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbyreducestage}
				\caption{Reduce Stage Completion Time\newline}
				\label{fig:reducestage}	
			\end{minipage}
		\end{subfigure}
		\vspace{-1em}
		\caption{Stage Completion Time of\newline Single Shuffle Test}
		\label{fig:singleshuffle}
	\end{minipage}	
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbymaptask}
				\caption{Median Task in Map Stages}
				\label{fig:maptask}
			\end{minipage}

			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbyreducetask}
				\caption{Median Task in Reduce Stages\newline}
				\label{fig:reducetask}
			\end{minipage}
		\end{subfigure}
		\vspace{-1em}
		\caption{Median Task Completion\newline Time of Single Shuffle Test}
		\label{fig:singleshuffletask}
	\end{minipage}	
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\vspace{-0.5em}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/tera}
				\caption{Reduce Stage of First Shuffle}
				\label{fig:terasort}
			\end{minipage}

			\begin{minipage}{\linewidth}
				\vspace{0.5em}
				\includegraphics[width=\linewidth]{fig/tera_shuffle}
				\caption{Network Traffic of Second Shuffle}
				\label{fig:terashuffle}
			\end{minipage}
		\end{subfigure}
		% \vspace{0.1em}
		\caption{Terasort Evaluation}
	\end{minipage}
\end{figure*}

@@

In the reduce task, most of the shuffle overhead is introduced by network transfer delay. 
By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
The in-memory cache of shuffle data further reduces the shuffle read time. 
As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
In addition, the heuristic algorithm can achieve a balanced pre-scheduling result, thus providing ~$80\%$ improvement in reduce stage completion time (Figure \ref{fig:reducestage}).

@@

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure*}
	\centering
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
		\caption{\color{blue}Hadoop MapReduce with SCache}
		\label{fig:hadoop_terasort_scache}
	\end{subfigure}
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
		\caption{\color{blue}Hadoop MapReduce without SCache}
		\label{fig:hadoop_terasort_origin}
	\end{subfigure}
	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
	\label{fig:hadoop_terasort}
\end{figure*}
\begin{figure*}
	\centering
	\includegraphics[width=.9\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

@@

\begin{figure}
    \centering
    \begin{minipage}{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
        \caption{\color{blue}Hadoop MapReduce Terasort completion time}
		\label{fig:hadoop_terasort_time}
    \end{minipage}\hfill
    \begin{minipage}{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/sampling} % second figure itself
        \caption{Sampling Overhead}
		\label{fig:sampling}
    \end{minipage}
\end{figure}

### 2019-03-26 jpdc/tex/impl.tex
Add jpdc.

% {\color{red}
% When a Spark job starts, the DAG will be first generated. 
% During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
% }
{\color{blue}
When a DAG job is submitted, the DAG information will be generated in framework task scheduler. 
Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
}
For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.  If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{blue}computing job}. We will elaborate the sampling procedure in the Section \ref{sampling}.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Heuristic MinHeap Scheduling for Single Shuffle}
% \label{hminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
% 		\State $m\gets$ partition number of map tasks
% 		\State $R\gets$ sort $p\_reduces$ by size in descending order
% 		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
% 		\State $idx\gets$ len$\left(R\right) - 1$
% 		\While{$idx \geq 0$}
% 		\Comment{Schedule reduces by MinHeap}
% 		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
% 		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
% 		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
% 		\State Sift down $M\left[0\right]$ by $size$
% 		\State $idx\gets idx-1$
% 		\EndWhile
% 		\State $max\gets$ maximum size in $M$
% 		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
% 		\ForAll{$reduce$ in $R$}
% 		\Comment{Heuristic swap by locality}
% 			\If{$reduce.assigned\_id \neq reduce.host\_id$}
% 				\State $p\gets reduce.prob$
% 				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
% 				\State $upper\_bound \gets \left(1 + norm\right) \times max$
% 				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
% 			\EndIf
% 		\EndFor
% 		% \Comment{$m$ is the number of input data}
% 		% \Comment{$r$ is partition number of reduces}
% 		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
% 		% \Comment{$c$ is $r*m$ array of composition data}
% 		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
% 		\Return $M$
% 	\EndProcedure
% 	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
% 		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
% 		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
% 		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
% 		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
% 		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
% 		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
% 			\qquad \; $size\_assigned\leq upper\_bound$}
% 			\State Swap $candidates$ and $reduce$
% 			\State Update $size$ in $M$
% 			\State Update $assigned\_host$ in $candidates$ and $reduce$
% 		\EndIf
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy. 
After that, the slot will be released (without being blocked on disk operations).
When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
% After that, when a map task is finished, each node will receive a broadcast message. 
SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After modification, DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
% \label{mhminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
% 		\State $m\gets$ partition number of map tasks
% 		\Comment $shuffles$ is the previous schedule result 
% 		\ForAll{$r$ in $p\_reduces$}
% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
% 			\EndIf
% 		\EndFor
% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
% 		\ForAll{$host\_id$ in $M$}
% 			\Comment Re-shuffle
% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
% 				\State Re-shuffle data to $host$
% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
% 				\EndIf
% 			\EndFor
% 		\EndFor
% 		\Return $M$
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

@@

\begin{figure}
	\centering
	\begin{minipage}{.47\textwidth}
		\centering
		\includegraphics[width=\linewidth]{fig/architecture}
		\caption{\color{blue}SCache Architecture}
		\label{fig:architecture}
		% \vspace{-0.5em}
	\end{minipage}\hfill
	\begin{minipage}{.42\textwidth}
		\centering
		\includegraphics[width=\linewidth]{fig/sample}
		\caption{Reservoir Sampling of One Partition}
		\label{fig:sample}
		% \vspace{-1em}
	\end{minipage}
\end{figure}

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires the modification on DAG frameworks. SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify two parts of the frameworks: (a) The DAG scheduler should provide the DAG information and follow the pre-scheduled result of SCache; (b) The shuffle data should be transferred to SCache Storage Management.

@@

\subsection{Fault tolerance}\label{fault}
Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
If a failure happened inside the SCache worker, SCache daemon could block the shuffle write/read operations until the worker process restarted without violating the correctness of DAG computing.
A possible way to handle this failure is selecting some backup nodes to store replications. 
But the replications can introduce a significant network overhead \cite{availability}.  
Currently, we left the sever faults (e.g., the failure of a node) to the DAG frameworks. 
We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
Meanwhile, SCache can still provide shuffle optimization during the recovery.

>>>>

% {\color{red}
% When a Spark job starts, the DAG will be first generated. 
% During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
% }
{\color{blue}
When a DAG job is submitted, the DAG information is generated in framework task scheduler. 
Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
}
For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.  If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{blue}computing job}. We will elaborate the sampling procedure in the Section \ref{sampling}.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Heuristic MinHeap Scheduling for Single Shuffle}
% \label{hminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
% 		\State $m\gets$ partition number of map tasks
% 		\State $R\gets$ sort $p\_reduces$ by size in descending order
% 		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
% 		\State $idx\gets$ len$\left(R\right) - 1$
% 		\While{$idx \geq 0$}
% 		\Comment{Schedule reduces by MinHeap}
% 		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
% 		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
% 		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
% 		\State Sift down $M\left[0\right]$ by $size$
% 		\State $idx\gets idx-1$
% 		\EndWhile
% 		\State $max\gets$ maximum size in $M$
% 		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
% 		\ForAll{$reduce$ in $R$}
% 		\Comment{Heuristic swap by locality}
% 			\If{$reduce.assigned\_id \neq reduce.host\_id$}
% 				\State $p\gets reduce.prob$
% 				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
% 				\State $upper\_bound \gets \left(1 + norm\right) \times max$
% 				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
% 			\EndIf
% 		\EndFor
% 		% \Comment{$m$ is the number of input data}
% 		% \Comment{$r$ is partition number of reduces}
% 		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
% 		% \Comment{$c$ is $r*m$ array of composition data}
% 		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
% 		\Return $M$
% 	\EndProcedure
% 	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
% 		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
% 		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
% 		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
% 		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
% 		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
% 		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
% 			\qquad \; $size\_assigned\leq upper\_bound$}
% 			\State Swap $candidates$ and $reduce$
% 			\State Update $size$ in $M$
% 			\State Update $assigned\_host$ in $candidates$ and $reduce$
% 		\EndIf
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy. 
After that, the slot will be released (without being blocked on disk operations).
When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
% After that, when a map task is finished, each node will receive a broadcast message. 
SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force the DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After modification, DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
% \begin{minipage}{\columnwidth}
% \begin{algorithm}[H]
% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
% \label{mhminheap}
% 	\begin{algorithmic}[1]
% 	\small
% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
% 		\State $m\gets$ partition number of map tasks
% 		\Comment $shuffles$ is the previous schedule result 
% 		\ForAll{$r$ in $p\_reduces$}
% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
% 			\EndIf
% 		\EndFor
% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
% 		\ForAll{$host\_id$ in $M$}
% 			\Comment Re-shuffle
% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
% 				\State Re-shuffle data to $host$
% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
% 				\EndIf
% 			\EndFor
% 		\EndFor
% 		\Return $M$
% 	\EndProcedure
% 	\end{algorithmic}
% \end{algorithm}
% \end{minipage}

@@

\begin{figure}
	\centering
	\begin{minipage}{.4\textwidth}
		\centering
		\includegraphics[width=\linewidth]{fig/architecture}
		\caption{\color{blue}SCache Architecture}
		\label{fig:architecture}
		% \vspace{-0.5em}
	\end{minipage}\hfill
	\begin{minipage}{.4\textwidth}
		\centering
		\includegraphics[width=\linewidth]{fig/sample}
		\caption{Reservoir Sampling of One Partition}
		\label{fig:sample}
		% \vspace{-1em}
	\end{minipage}
\end{figure}

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires the modification on the DAG frameworks. SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify two parts of the frameworks: (a) The DAG scheduler should provide the DAG information and follow the pre-scheduled result of SCache; (b) The shuffle data should be transferred to SCache Storage Management.

@@

\subsection{Fault tolerance}\label{fault}
Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
If a failure happened inside the SCache worker, SCache daemon could block the shuffle write/read operations until the worker process restarted without violating the correctness of the DAG computing.
A possible way to handle this failure is selecting some backup nodes to store replications. 
But the replications can introduce a significant network overhead \cite{availability}.  
Currently, we left the sever faults (e.g., the failure of a node) to the DAG frameworks. 
We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
Meanwhile, SCache can still provide shuffle optimization during the recovery.
